Presentation Title

### 2017-06-18 thesis/chapters/ch2-model.tex
Better Byzantine consensus background

\subsection{Consensus Protocol}\label{sec:overview-cons}
Before describing our consensus protocol, we take a brief detour to explain asynchronous common subset primitive and contrast it with other well known primitives.
It is a fundamental building block of our consensus protocol.

\subsubsection*{Asynchronous common subset}
TODO give history/background of ACS
Asynchronous common subset (ACS) is an especially useful primitive for blockchain systems.
It allows any party to propose a value and the result is the set union of all the proposed values by the majority.
Concretely, ACS needs to satisfy the following properties (adapted from~\cite{miller2016honey}).
\begin{definition}
\label{def:acs}
\textbf{\emph{Properties of ACS}}

\begin{enumerate}
    \item \emph{Validity}:
        If any correct party outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ parties.
    \item \emph{Agreement}:
        If a correct party outputs $C$, then every party outputs $C$.
    \item \emph{Totality}:
        If $n - f$ party receive an input, then all correct parties produce an output.
\end{enumerate}
\end{definition}

ACS has the nice property of censorship resiliance when compared to other consensus algorithms.
For instance, Hyperledger and Tender mint uses Practical Byzantine Fault Tolerance (PBFT) as their consensus algorithm.
In PBFT, a leader is elected, if the leader is malicious but follows the protocol, then it can selectivly filter transactions.
In contract, every party in ACS are involved in the proposal phase,
and it guarantees that if $n - 2t$ parties propose the same transaction, then it must be in the agreed output.

The main drawback with ACS and other BFT protocols is the high message complexity.
Typically, such protocols have the complexity of $O(n^2)$, where $n$ is the number of parties.
Hence, it may work with a small number of nodes,
but it is infeasible for blockchain systems where thousands of nodes are involved.

\subsubsection*{Consensus Protocol} 
The consensus protocol runs continuously in rounds
because a blockchain systems always need to reach consensus on new values, which are CP blocks in our case.
This can be seen as running infinitly many rounds of some Byzantine consensus algorithm,
starting a new execution immediately after the previous one is completed.

As we mentioned earlier, the high message complexity prohibits us from running a Byzantine consensus algorithm on a large network.
Thus, for every round, we randomly select some node---called facilitators---to collect CP blocks and use them as the proposal.
The facilitators are elected using a \emph{luck value}, which is computed using $H(\C_r || pk_i)$,
where $\C_r$ is the consensus result in round $r$ and $pk_i$ is the public key of $i$.
Intuitively, the election is guaranteed to be random 
because the output of a cryptographically secure hash function is unpredictable and $\C_r$ cannot be determined in advance.

@@

We proceed to describe the protocol step by step.
Starting with the bootstrap phase and then moving on to the actual consensus phase.

>>>>

\subsection{Consensus Protocol}\label{sec:overview-cons}

% The consensus protocol uses an existing Byzantine consensus algorithm (explained in detail in \Cref{sec:xyz}) and runs it continuously in rounds.
The consensus protocol can be seen as a technique of running infinitly many rounds of some 
Byzantine consensus algorithm\footnote{More accuratly it is ACS or asynchronous subset consensus, we describe ACS in \Cref{sec:acs}.},
starting a new execution immediately after the previous one is completed.
This is necessary because blockchain systems always need to reach consensus on new values, or CP blocks in our case.

The high message complexity of Byzantine consensus algorithms prohibits us from running it on a large network.
Thus, for every round, we randomly select some node---called facilitators---to collect CP blocks and use them as the proposal.
The facilitators are elected using a \emph{luck value}, which is computed using $H(\C_r || pk_i)$,
where $\C_r$ is the consensus result (a set of CP blocks) in round $r$ and $pk_i$ is the public key of $i$.
Intuitively, the election is guaranteed to be random 
because the output of a cryptographically secure hash function is unpredictable and $\C_r$ cannot be determined in advance.

@@

Before describing the protocol in detail, we take a brief detour to give background on the Byzantine consensus algorithm we use in the consensus protocol.
% Starting with the bootstrap phase and then moving on to the actual consensus phase.

\subsection{Background on Asynchronous Subset Consensus}

The best way to explain asynchronous subset consensus (ACS) is to contrast it with the typical Byzantine consensus problem.
We adapt the description from~\cite{podc}.
%The Byzantine consensus problem is a classical problem is distributed systems literature.
%It is first described by Leslie Lamport as the Byzantine general's problem in 1982~\cite{lamport1982byzantine}.
%Byzantine consensus is described as follows (adapted from ).
\begin{definition}
\textbf{\emph{Byzantine Consensus}}

There are $n$ nodes, of which at most $t$ might experience Byzantine fault.
Node $i$ starts with an input value $v_i$.
The nodes must decide for one of  those values, satisfying the the following.
\begin{enumerate}
    \item \emph{Agreement:}
        All correct nodes decide for the same value.
    \item \emph{Validity:}
        The decision value must be the input value of a node.
    \item \emph{Termination:}
        All correct nodes terminate in finite time.
\end{enumerate}
\end{definition}
A node under Byzantine fault means that it can have arbitrary behaviour.
For example not sending message or colluding with other Byzantine nodes to undermine the entire system.
Note that the decision is on a single value.
This is in contrast to ACS which we describe next.

ACS shares many similarities with Byzantine consensus.
But it is an especially useful primitive for blockchain systems.
It allows any party to propose a value and the result is the set union of all the proposed values by the majority.
This is the primary difference with Byzantine consensus.
Concretely, ACS needs to satisfy the following properties (adapted from~\cite{miller2016honey}).
\begin{definition}
\label{def:acs}
\textbf{\emph{Asynchronous Subset Consensus}}

There are $n$ nodes, of which at most $t$ might experience Byzantine fault.
Node $i$ starts with an non-empty set of input values $C_i$.
The nodes must decide an output $C$, satisfying the following.
\begin{enumerate}
    \item \emph{Validity:}
        If any correct party outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ parties.
    \item \emph{Agreement:}
        If a correct party outputs $C$, then every party outputs $C$.
    \item \emph{Totality:}
        If $n - t$ party receive an input, then all correct parties produce an output.
\end{enumerate}
\end{definition}
ACS has the nice property of censorship resiliance when compared to other consensus algorithms.
For instance, Hyperledger and Tender mint uses Practical Byzantine Fault Tolerance (PBFT) as their consensus algorithm.
In PBFT, a leader is elected, if the leader is malicious but follows the protocol, then it can selectivly filter transactions.
In contract, every party in ACS are involved in the proposal phase,
and it guarantees that if $n - 2t$ parties propose the same transaction, then it must be in the agreed output.
Thus, some value is submitted to at least $n - 2t$ nodes, it is guaranteed to be in the consensus result.
For a detailed description of ACS we refer to the HoneyBadgerBFT work~\cite{miller2016honey}.

The main drawback with ACS and also Byzantine consensus algorithms is the high message complexity.
Typically, such protocols have the complexity of $O(n^2)$, where $n$ is the number of parties.
Hence, it may work with a small number of nodes,
but it is infeasible for blockchain systems where thousands of nodes are involved.

### 2017-06-18 thesis/chapters/ch5-related-work.tex
Better Byzantine consensus background

Having analysed our system both theoretically and experimentally,
we dedicate this chapter on comparing our results with related work.
Blockchain technology has seen a surge in recent years from both the industry and academia.
There are many approaches and innovation.
We classify by their consensus approach and divide them into the following categories: 
\begin{enumerate}
    \item classical blockchain systems,
    \item Byzantine fault tolerance consensus based consensus,
    \item hybrid systems and
    \item blockchain without global consensus.
\end{enumerate}

@@

\section{Byzantine Fault Tolerance Consensus Based Systems}

The Byzantine fault tolerance problem is a classical problem is distributed systems literature.
It is first described by Leslie Lamport as the Byzantine general's problem in 1982~\cite{lamport1982byzantine}.

>>>>

Having analysed our system both theoretically and experimentally,
we dedicate this chapter on comparing our results with related work.
Blockchain technology has seen a surge in recent years from both the industry and academia.
There are many approaches and innovation.
We classify by their consensus approach and divide them into the following categories: 
\begin{enumerate}
    \item classical blockchain systems,
    \item Byzantine consensus based consensus,
    \item hybrid systems and
    \item blockchain without global consensus.
\end{enumerate}

@@

\section{Byzantine Consensus Based Systems}
